Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-08-21 prob.tex
prob.tex Typed two possible plans...

\section{Quantum Computing on Quantum Interval-valued Probability Measures}

@@

\subsection{Time Evolution and Tensor Product}

@@

>>>>

\section{(One possible branch) Discrete Quantum Theory}

\subsection{Discrete Quantum Real-valued Probability Measures}

Killed by John... Need to be typed...

\subsection{Discrete Quantum Interval-valued Probability Measures}

\yutsung{Because theorem~\ref{def:EmptyCoreQuantumInterval-valuedProbability}
gives a negative result, our original plan was to put the Mermin v.s.
Meyer debate here, and move on to the discrete quantum probability
measure. Then, discrete real-valued quantum probability measures are
expected to fail because of John's proof, and we hope discrete interval-valued
quantum probability measure can work in some sense?

I just want to confirm whether we want to keep our original plan to
move on to the discrete quantum probability measure. Because we don't
really use $\mathbb{C}$ in example~\ref{ex:three-dimensional-three-value},
I could expect example~\ref{ex:three-dimensional-three-value} is
highly likely to serve as an counterexample for discrete interval-valued
quantum probability measure...}

\section{(Another possible branch) Quantum Computing on Quantum Interval-valued
Probability Measures}

@@

\subsection{Time Evolution}

@@

\subsection{Tensor Product and Partial Measurement}

\yutsung{Quantum Fubini Theorem? This might be hard?}
